Towards Practical Probabilistic Programming

### 2018-10-31 abstract/paper.tex
another word

While we enjoy the ease and efficiency of
\texttt{infergo}-based inference in our production environment,
we view \texttt{infergo} as a reference implementation rather than
as the only solution, and encourage the community to equip other
general-purpose languages with similar inference facilities,
which, we believe, will make wide adoption of probabilistic
programming more likely.
be

>>>>

While we enjoy the ease and efficiency of \texttt{infergo}-based
inference in our production environment, we view
\texttt{infergo} as a reference implementation rather than as
the only recommended solution, and encourage the community to
equip other general-purpose languages with similar inference
facilities, which, we believe, will make wide adoption of
probabilistic programming more likely.
